final_project_draft

### 2022-04-13 draft.Rmd
April 13th graded before class commit. Made some changes and worked with new data set.

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "Is There Any Political Party Receiving More Support From Charles Johnson?",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)))

table <- data.frame(Party = rep(c("Republican", "Bipartisan, but mostly Republican",
                                "Democrat", each = 1),
                              Count = rep(c("207", "4", "2"), 1)))
table

@@

ggplot(data = recipients, aes(x = recipient, y = n, colour = Party)) +
  geom_point() +
  geom_segment(aes(x = recipient, xend = recipient, y = 0, yend = n)) +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

>>>>

## Written Description 
The general purpose of this project is to curate many different data visualizations using a variety of data sets. I want to create a personal website using blogdown to share these data visualizations. I decided to use data that was interesting to me, and found that I was most interested in data examining the political donations made by professional sport team owners from different leagues.

Data Ethics: 
* Political donations are public information; scraped the data from Kaggle, did not realize until today (April 10th) that fivethirtyeright actually published a piece using this data but luckily the visualizations that I have already made are different from those on fivethirtyeight 
* did not exclude N/A for a party affiliation point because I did not think there was any reason other than making the legend look better

Expressing Variability:
* Use scatter plots to show variability in data, and use bar plots to show the count of categorical variables

Motivation and Grammar of Graphics:
* Used theme() for the style of my visualizations

@@

ggplot(data = cj_party, aes(x = party, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  scale_fill_viridis_d(option = "plasma") +
  labs(title = "Party Affiliation of Political Donations Made by Charles Johnson",
       x = " ",
       y = "Count of Donations") +
  theme(legend.position = "bottom",
        plot.title = element_text(family = "mono",
                                  face = "bold",
                                  hjust = 0.5,
                                  size = 13,
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks.y = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_text(family = "mono",
                                    size = 9,
                                    face = "italic",
                                    margin = margin(t = 20)))

cj_party2 <- cj_party %>% select(n, party)

@@

ggplot(data = recipients, aes(x = recipient, y = n, fill = Party)) +
  geom_col() +
  coord_flip() +
  labs(x = " ",
       y = "Count of Donations") +
  labs(title = "Organizations Receiving Most Donations Among All Owners") +
  scale_fill_brewer(palette = "Dark2") +
  theme(legend.position = "bottom") +
  scale_x_discrete(labels = new_names) +
  theme(plot.title = element_text(family = "mono",
                                  face = "bold",
                                  margin = margin(c(t = 50,
                                                    b = 50)),
                                  vjust = 10),
        axis.text = element_text(family = "mono"),
        axis.title = element_text(family = "mono",
                                  size = 8),
        axis.title.x = element_text(size = 10,
                                    margin = margin(t = 20,
                                                    b = 10)),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
         legend.box.background = element_rect())

@@

## Forbes Billionaires 2021

## Potential questions:
## Who are the most recent top 10 billionaires: name v net worth ?

## look at average age of billionaires in general/maybe by country?: do billionaires tend to be very old or are there more billionaires on the younger side?

## Look at most prevalent industry of billionaires: mostly technology or something else?

## How many billionaires in each country: mostly capitalist or other economic systems?

## Average networth of billionaires by industry?

## Top 10 Billionaires coloured by industry (Forbes 2021 Billionaires)
```{r}
billionaires <- read_csv("data/Billionaire.csv")
billionaires

top10 <- billionaires %>% filter(Rank <= 10) %>%
  mutate(NetWorth = parse_number(NetWorth)) %>%
  mutate(order = fct_reorder(.f = Name, .x = NetWorth)) %>%
  mutate(Industry = fct_relevel(Industry, c("Technology",
                                            "Automotive",
                                            "Fashion & Retail", 
                                            "Finance & Investments", 
                                            "Diversified")))
top10

new_names2 <- c("Mukesh Ambani", "Sergey Brin", "Larry Page", "Larry Ellison",
                "Warren Buffett", "Mark Zuckerberg", "Bill Gates", 
                "Bernard Arnault & Family", "Elon Musk", "Jeff Bezos")

ggplot(data = top10, aes(x = order, y = NetWorth, fill = Industry)) +
  geom_col() +
  coord_flip() +
  labs(x = "Billionaire Name", 
       y = "Net Worth",
       caption = "Measured in Billions",
       colour = "Industry",
       title = "2021 Forbes Billionaires with the Highest Net Worth") +
  scale_fill_viridis_d() +
  scale_x_discrete(labels = new_names2) +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        axis.ticks = element_blank(),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        legend.title = element_text(family = "mono",
                                    face = "bold"),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        plot.caption = element_text(family = "mono",
                                    face = "italic"))
```

## Forbes Billionaire 2021 2.0 Data Set
```{r}
forbes_billionaires <- read_csv("data/forbes_billionaires.csv")
forbes_billionaires

country <- forbes_billionaires %>% group_by(Country) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
country

forbes_billionaires_age <- forbes_billionaires %>%
  mutate(age = as.numeric(Age)) %>%
  select(age, everything())

countries_10 <- forbes_billionaires_age %>% filter(Country == "United States" |
           Country == "China" |
           Country == "India" |
           Country == "Germany" |
           Country == "Russia" |
           Country == "Hong Kong" |
           Country == "Brazil" |
           Country == "Canada" |
           Country == "United Kingdom" |
           Country == "Italy")

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point() +
  coord_flip()

check <- countries_10 %>% filter(Age < 25 | Age > 90)

filter <- countries_10 %>% filter(!is.na(age))
filter2 <- filter %>% group_by(Country) %>%
  summarise(Average = mean(age))

ggplot(data = countries_10, aes(x = Country, y = age)) +
  geom_point(alpha = 0.2) +
  coord_flip() +
  geom_point(data = filter2, aes(y = Average, colour = "Mean Age"),
             size = 2.5) +
  scale_colour_manual(values = c("Mean Age" = "red")) +
  labs(x = "Country", 
       y = "Age",
       title = "Average Age of Billionaires by Country",
       caption = "The Red Points Indicate the Average Age of Billionaires From Each
       Country") +
  theme(axis.title = element_text(family = "mono",
                                  face = "bold"),
        axis.text = element_text(family = "mono"),
        plot.title = element_text(family = "mono",
                                  face = "bold"),
        axis.ticks = element_blank(),
        legend.title = element_blank(),
        legend.text = element_text(family = "mono",
                                   face = "italic"),
        legend.position = "none",
        plot.caption = element_text(family = "mono",
                                    size = 9,
                                    face = "italic")) 
```

## Playing Around with New Variables 
```{r}
self_made <- forbes_billionaires %>% group_by(Self_made) %>%
  summarise(n = n())

ggplot(data = forbes_billionaires, aes(x = Self_made)) +
  geom_bar()

industry <- billionaires %>% group_by(Industry) %>%
  summarise(n = n()) %>%
  arrange(desc(n))
industry

combined_billionaires <- left_join(forbes_billionaires, billionaires, by = c("Name" = "Name"))
combined_billionaires

usa_billionaires <- combined_billionaires %>% filter(Country.x == "United States")
ggplot(data = usa_billionaires, aes(x = Self_made)) +
  geom_bar()

forbes_billionaires %>% group_by(Status) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

tidy_education <- forbes_billionaires %>% 
  separate(col = Education, into = c("Degree", "University"),
                                 sep = ", ") %>%
  select(Degree, University, everything())
tidy_education

tidy_education %>% group_by(Degree) %>%
  summarise(n = n()) %>%
  arrange(desc(n))

tidy_education2 <- tidy_education %>% filter(Degree == "Bachelor of Arts/Science" |
                          Degree == "Master of Business Administration" |
                          Degree == "Master of Science" |
                          Degree == "Drop Out" |
                          Degree == "Bachelor of Science" |
                          Degree == "Bachelor of Science in Engineering" |
                          Degree == "Doctorate" |
                          Degree == "Diploma" |
                          Degree == "Bachelor of Arts/Economic")

ggplot(data = tidy_education2, aes(x = Degree, y = NetWorth)) +
  geom_point() +
  coord_flip() +
  labs(x = "Education Level",
       y = "Net Worth")
```

## Forbes Billionaire 2021 3.0 Data Set 
```{r}
forbes_billionaires_geo <- read_csv("data/forbes_billionaires_geo.csv")
forbes_billionaires_geo 
```

## Billionaires Age in Countries with most billionaires 
```{r}

ggplot(data = countries_10, aes(x = Country, y = Age)) +
  geom_point() +
  coord_flip() +
  geom_point(data = average_top10_countries, aes(y = Average, colour = "Average Billionaire Age")) +
  scale_colour_manual(values = c("Average Billionaire Age" = "red"))
```
